Gap

### 2020-01-04 gap/article/llncs2e/article.tex
Added article skeleton

\begin{document}
%
\title{Solving Gap\thanks{Supported by no one lol}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{João Pedro Pinheiro de Lacerda Campos\inst{1} \and
Leonardo Fernandes Moura\inst{1}}
%
\authorrunning{J. Campos L. Moura}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculdade de Engenharia da Universidade do Porto,
Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL
\email{feup@fe.up.pt}\\
\url{http://www.fe.up.pt}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

\begin{document}
%
\title{Gap}

\subtitle{Puzzle solving using Prolog constraints}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{João Pedro Pinheiro de Lacerda Campos\inst{1,2} \and
Leonardo Fernandes Moura\inst{1,2}}
%
\authorrunning{J. Campos L. Moura}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%

\institute{
Faculdade de Engenharia da Universidade do Porto,
Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL
\email{feup@fe.up.pt}\\
\url{http://www.fe.up.pt} \and
Logical Programing Course, Class 3MIEIC03, Group Gap Puzzle\_5}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

\section{Introduction}

\section{Problem Description}

\section{Approach}

\subsection{Decision Variables}

\subsection{Constraints}

\subsection{Evaluation Function}

\section{Search Strategy}

\section{Solution Presentation}

\section{Results}

\section{Conclusions and Future Work}

\begin{thebibliography}{8}
    \bibitem{ref_article1}
    Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

    \bibitem{ref_url1}
    LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
    Oct 2017
    \end{thebibliography}

% Article sampkes  REMOVE IN THE END
\section{Introduction}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.
